Jeff Goldsmith

### 2017-04-11 best_pubs.Rmd
only 5 papers...

Below is a collection of papers that best represents my work in statistical methods development and transdisciplinary research. For each, there is a brief synopsis and a link to download a PDF of the paper. A comprehensive list of all my publications is [here](papers.html).
<br><br>

@@

**J. Goldsmith**, V. Zipunnikov, J. Schrack (2015).
Generalized Multilevel Functional-on-Scalar Regression and Principal Component Analysis.
<i> Biometrics, </i>
<b>71</b> 344-353.
[[pdf](BestPubs/GenMFPCA.pdf)].

#### Variable Selection in the Functional Linear Concurrent Model

@@

**J. Goldsmith**, J. E. Schwartz.
Variable Selection in the Functional Linear Concurrent Model (2017+).
<i> Statistics in Medicine, </i>
accepted.
[[pdf](BestPubs/VBVS.pdf)].

@@

**J. Goldsmith**, T. Kitago (2016).
Assessing Systematic Effects of Stroke on Motor Control using Hierarchical Function-on-Scalar Regression.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>65</b> 215-236.
[[pdf](BestPubs/BayesPFSR.pdf)].

@@

D. Backenroth, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago.
Modeling motor learning using heteroskedastic functional principal components analysis.
<i> Journal of the American Statistical Association, </i> acceptable after major revisions.
[[pdf](BestPubs/MotorLearning.pdf)].

@@

**J. Goldsmith**, S. Greven, C. M. Crainiceanu (2013).
Corrected Confidence Bands for Functional Data Using Principal Components.
<i> Biometrics, </i>
<b>69</b> 41-51.
[[pdf](BestPubs/FPCA_Bands.pdf)].

>>>>

Below is a collection of papers that best represents my work in statistical methods development and transdisciplinary research. For each, there is a brief synopsis, a full citation, and a link to download a PDF of the paper.

A comprehensive list of all my publications is [here](papers.html).
<br><br>

@@

**J. Goldsmith**, V. Zipunnikov, J. Schrack (2015).
Generalized Multilevel Functional-on-Scalar Regression and Principal Component Analysis.
<i> Biometrics, </i>
<b>71</b> 344-353.
[[pdf](BestPubs/GenMFPCA.pdf)].
<br><br>
<!--
#### Variable Selection in the Functional Linear Concurrent Model

@@

**J. Goldsmith**, J. E. Schwartz.
Variable Selection in the Functional Linear Concurrent Model (2017+).
<i> Statistics in Medicine, </i>
accepted.
[[pdf](BestPubs/VBVS.pdf)].
<br><br>
-->

@@

**J. Goldsmith**, T. Kitago (2016).
Assessing Systematic Effects of Stroke on Motor Control using Hierarchical Function-on-Scalar Regression.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>65</b> 215-236.
[[pdf](BestPubs/BayesPFSR.pdf)].
<br><br>

@@

D. Backenroth, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago.
Modeling motor learning using heteroskedastic functional principal components analysis.
<i> Journal of the American Statistical Association, </i> acceptable after major revisions.
[[pdf](BestPubs/MotorLearning.pdf)].
<br><br>

@@

**J. Goldsmith**, S. Greven, C. M. Crainiceanu (2013).
Corrected Confidence Bands for Functional Data Using Principal Components.
<i> Biometrics, </i>
<b>69</b> 41-51.
[[pdf](BestPubs/FPCA_Bands.pdf)].
<br><br>
